On Star Formation at Dynamical Resonances of the Bar

### 2020-01-19 paper/ms.tex
Update methods section

\newcommand{\arepo}{\textsc{Arepo}}

@@

In our simulations we will reach $\sim10^3\,\Msun$ mass resolution. `

>>>>

\newcommand{\arepo}{\textsc{Arepo}}
\newcommand{\smuggle}{\textsc{SMUGGLE}}

@@

In our simulations we will reach $\sim10^3\,\Msun$ mass resolution. As a
result, the cold phase of the interstellar medium (ISM) is well-resolved
(\textcolor{red}{cite}), and an appropriate physical model which account for
the processes occuring at these scales must be used. In this vein, we use the
state-of-the-art model \smuggle{} \citep{2019MNRAS.489.4233M}. A detailed
description of the model is presented in \citet{2019MNRAS.489.4233M}, but we
summarize the salient components here.

Standard cooling processes are accounted for using tabulated \textsc{cloudy}
calculations, described in detail in \citet{2013MNRAS.436.3031V}. In addition
to standard channels, metal line, fine-structure, and molecular cooling
processes are also accounted for, allowing the gas to reach
$\sim10\,\text{K}$, as well as self-shielding for high-density gas. Cosmic ray
and photoelectric heating are also taken into account. Star formation follows
a standard probabilistic approach \citep{2003MNRAS.339..289S}, with the star
formation efficiency ($\epsilon$) set to $0.01$ and additional density and
viriality conditions. Finally, stellar feedback is accounted for in three
different channels: supernovae, young massive stellar radiation, and stellar
winds from OB and AGB stars.

The model used here is similar to the one used first by
\citet{2011MNRAS.410.1391A, 2013ApJ...770...25A} and by the Feedback In
Realistic Environments (FIRE) collaboration \citep{2011MNRAS.417..950H,
2014MNRAS.445..581H, 2018MNRAS.480..800H}, with some key differences discussed
in \citet{2019MNRAS.489.4233M}. One drawback of the \smuggle{} method is that
radiation is not self-consistently tracked and evolved, and therefore
radiation feedback must be implemented in an approximate manner. An extension
of \smuggle{} which explicitly tracks the radiation field as an additional
fluid component \citep{2019arXiv191014041K} based upon \areport{}
\citep{2019MNRAS.485..117K} is available. We plan to use this module in the
future.

% Standard cooling processes from hydrogen and helium undergoing two-body
% interactions, Compton cooling of cosmic microwave background photons, and
% photoionization from a uniform UV background are accounted for using tabulated
% \textsc{CLOUDY} calculations, described in detail in
% \citet{2013MNRAS.436.3031V}. In addition to these processes, metal line,
% fine-structure, and molecular cooling processes are accounted for, in order to
% allow the gas to reach $\sim 10\,\text{K}$. At high densities, self-shielding
% of the gas is accounted for using an analytic formula. Cosmic ray and
% photoelectric heating are also taken into account, important for the thermal
% stability of the cold and warm phases.

% Star formation follows a standard probabilistic approach
% \citep{2003MNRAS.339..289S}, where star particles are created and assumed to
% be a coeval population following a \citet{2001ApJ...554.1274C} initial mass
% function. Star formation efficiency ($\epsilon$) is assumed to be $0.01$. An
% additional density threshold of $100\,\text{cm}^{-3}$ and a condition on a gas
% cell to be sub-virial ($\alpha < 1$) and thus prone to gravitational collapse
% are applied.

% Finally, stellar feedback is accounted for in three different channels:
% supernovae, young massive stellar radiation, and stellar winds from OB and AGB
% stars.
